Timely Object Recognition

### 2012-06-01 writeups/nips12/evaluation.tex
paper
draft for mario

\todo{completely rework when settled on results story}

One simple heuristic value function that we can try is simply picking the action corresponding to the class presence variable $C_k$ with the highest probability.

We use one-vs-all deformable part-model classifiers on a HOG featurization of the image \cite{Felzenszwalb2010a}, with associated linear classification of the detections.

@@

To summarize \autoref{sec:}, we evaluate our system in the multi-class, multi-label detection regime.
We evaluate on a popular detection challenge task: the PASCAL VOC dataset \cite{pascal-voc-2010}.
As shown in \autoref{fig:dataset_stats}, the dataset exhibits a rather modest amount of class co-occurrence, which puts our model in a disadvantaged setting.
$60\%$ of the images in the training set have only one class; $30\%$ have two classes, $7\%$ have three classes, and almost none have more.

Using the 2007 version of the dataset, we train on the training and validation data and test on the test set.
We run our policies on all images in the test set, cutting off execution at $T_d$.

To evaluate performance at a given time, we gather all detections and the classification answers found to this point in all the recognition episodes.
As described before, we evaluate detection performance by averaging per-image performance in the multi-class regime.
We evaluate classification performance by pooling the ground truth across the dataset, in standard procedure.

We establish the baseline performance of our system by selecting actions randomly at each step.
The time setting for our evaluation is $T_s=0$, $T_d=20$ (in seconds).
As shown in Figure~\ref{fig:results_manual}, the random policy results in a roughly linear gain of performance vs. time.

To establish an upper bound on performance, we also plot the Oracle curve, obtained by re-ordering the actions with the hindsight of the results they produced.
Note that the curves turn downward in this setting: this is due to the different performance levels of the detectors: as the weaker detectors are inevitably run, they introduce more false positives and false negatives than true positives.

\begin{figure}[h!]
\centering
\subfloat[AP vs. Time curves]{\includegraphics[width=0.47\linewidth]
    {../figures/final1.png}} \hfill
\subfloat[Execution traces of different policies]{\includegraphics[draft,width=0.47\linewidth]
    {../figures/final1.png}}
  \label{fig:results1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.87\linewidth]
    {../figures/weights.pdf}
\caption{Weights}
\label{fig:weights}
\end{figure}

\begin{table}[t]
\caption{Results}
\label{tab:results}
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|}
\\ \hline \\
Bounds & Random & Fixed Order & RL w/ MRF & w/ GIST   & Oracle \\ \hline
(0,10) & 0.1191 & 0.2404      & 0.2664    & 0.2665    & 0.4638 \\ 
(0,20) & 0.2497 & 0.3421      & 0.3781    & 0.3824    & 0.4878 \\ 
(5,15) & 0      & 0           & 0         & 0         & 0      \\
\end{tabular}
\end{center}
\end{table}

Figure~\ref{fig:results1} also shows the performance of our policy with the heuristic value function and two inference models: the MRF model and a simple fixed-order model that follows the priors.
We can see that due to the dataset bias, the fixed-order policy performs well at first (the person class is disproportionately likely to be in the image), but is overtaken by the proper inference model as execution goes on.

A notable difference between the MRF inference model and the fixed-order model was in the weights learned: while the fixed-order model learned weights onto the bias feature only, the MRF inference model learned weights onto a mix of the entropy and probability features

>>>>

We evaluate our system on the multi-class, multi-label detection task as previously described.
Each detection episode takes an image and outputs detections with associated times, based on the order of actions taken.
We evaluate on a popular detection challenge task: the PASCAL VOC 2007 dataset \cite{pascal-voc-2010}.
As shown in \autoref{fig:dataset_stats}, the dataset exhibits a rather modest amount of class co-occurrence.

We learn weights on the training and validation sets, and run our policy on all images in the testing set.
The final evaluation pools all detections up to a certain time, and computes their multi-class AP per image, then averaging over all images.
This is done for different times to plot the AP vs. Time curve over the whole dataset.
The evaluation is slightly different that what is usually done (all detections for a class are pooled across the dataset), but has been used before \cite{Desai2009}.

For the detector actions, we use one-vs-all cascaded deformable part-model detectors on a HOG featurization of the image \cite{Felzenszwalb2010b}, with associated linear classification of the detections.
There are $20$ classes in the PASCAL challenge task, so there are $20$ detector actions.
Running a detector on a PASCAL image takes about $1$ second.
Additionally, we use a classifier from the scene-level GIST feature to class presence, for each class.
This is considered one action, and takes about $0.3$ seconds.

We test three different settings of the start and deadline times.
In the first one, the start time is immediate and execution is cut off at 20 seconds, which is enough time to run basically all actions.
In the second one, execution is cut off after only 10 seconds.
Lastly, we measure performance between 5 seconds and 15 seconds.
These operating points show how our method would behave when deployed in different conditions.

@@

\begin{figure}[h!]
\centering
\subfloat[AP vs. Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy, with start time of 5 seconds and deadline of 15 seconds.]{\includegraphics[width=0.47\linewidth]
    {../figures/final1_515.png}} \hfill
\subfloat[Execution traces of different policies]{\includegraphics[draft,width=0.47\linewidth]
    {../figures/final1.png}}
  \label{fig:results1}
\end{figure}

We establish the first baseline for our system by selecting actions randomly at each step.
As shown in Figure~\ref{fig:results1}, this \textbf{Random} policy results in a roughly linear gain of AP vs. time.
This is expected: the detectors are capable of obtaining a certain level of performance; if half the detectors are run, the expected performance level is half of the maximum level.

To establish an upper bound on performance, we plot the \textbf{Oracle} policy, obtained by re-ordering the actions with the hindsight of the results they produced.

We consider another baseline: selecting actions in a fixed order based on the value they bring to the AP vs. Time evaluation, which is roughly proportional to their occurrence probability.
We refer to this as \textbf{Fixed Order}.

Then there are our proposed systems, which the previous section thoroughly described: \textbf{RL w/ Direct} and \textbf{RL w/ MRF}.
In experiments, the two were not exceedingly different in performance, with the MRF model consistently performing slightly better.

In \autoref{fig:results1}, we can see that due to the dataset bias, the fixed-order policy performs well at first (as can be seen in \autoref{fig:dataset_stats}, the person class is disproportionately likely to be in the image), but is significantly overtaken by our model as execution goes on.

Lastly, we also evaluate the system that includes a GIST action; this always uses the MRF model to properly update the class probabilities with GIST observations.
This brings another boost in performance.
All results are shown in \autoref{tab:results}.

Additionally, we evaluated different settings of the discount parameter $\gamma$, and found that a mid-range value works best.
We only report results for that value on the test set.
\autoref{fig:weights} shows how changing $\gamma$ affects the learned weights: the GIST action is learned to never be taken in the greedy setting, because it does not nring any immediate detections results.
In the reinforcement learning setting, however (higher $\gamma$), GIST is learned to be taken for its value in quickly refining the class presence probabilities.

\begin{table}[t]
\caption{Results}
\label{tab:results}
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|}
\\ \hline \\
Bounds & Random & Fixed Order & RL w/ MRF & w/ GIST  & Oracle \\ \hline
(0,10) & 0.119  & 0.240       & 0.266     & \textbf{0.267}    & 0.464 \\ 
(0,20) & 0.250  & 0.342       & 0.378     & 0.382    & 0.488 \\ 
(5,15) & 0.257  & 0.362       & 0.418     & 0.420    & 0.530 \\
\end{tabular}
\end{center}
\end{table}

\todo{something about setting values?}

### 2012-06-01 writeups/nips12/introduction.tex
draft for mario

In recent years, the computer vision field has converged on a general method for object detection, and a standard evaluation of results.
In the evaluation ground truth, each object is assumed to belong to one of a fixed set of classes; its location is approximated by placing a bounding box around pixels belonging to it.
Large datasets of such human annotations are used for evaluation of detection algorithms~\cite{pascal-voc-2010,imagenet_cvpr09}.

With few exceptions, current detection systems are not inherently multi-class.
Instead, separate detectors are trained per class, and they are deployed and evaluated independently.
The evaluation of multi-class performance consists of averaging the per-class metrics.
State-of-the-art detection systems also do not generally make efficiency a goal.

\begin{figure}[ht!]
\center{\includegraphics[width=0.56\linewidth]
    {../figures/evaluation_thumbs.png}}
  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.}
  \label{fig:evaluation}
\end{figure}

There are of course many applications of object recogniition for which performance truly is time-sensitive.
In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
In large-scale detection system deployments, such as for image search, results need to be obtained quickly per image as the number of images to process is large and growing.
When processing large photo collection on end-user machines for immediate consumer navigation, the same is true.

In all these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.
Furthermore, the value of the answer depends largely on the target application.

A hypothetical recognition system for a vision-based advertising deployment presents a case study.
The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
The most rational detection strategy in such an environment should depend on all of these variables.

We argue that the key to tackling such problems of dynamic recognition resource allocation is to start asking a new question:
\emph{What is the best performance we can get on a budget?}
To answer it, we consider the evaluation metric of performance vs. time, shown in Figure~\ref{fig:evaluation} and discussed further in the text.

Our system takes various detectors and classifiers as black boxes, and derives a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.

>>>>

The computer vision field has converged on a general method for object detection, and a standard evaluation of results.
Efficiency is not a concern of the evaluation metrics, and the methods are not evaluated in an inherently multi-class setting.
However, in most real-world applications of object recogniition, performance is time-sensitive and inherently tied to the many-class nature of the world.

In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
In large-scale detection system deployments, such as for image search, results need to be obtained quickly per image as the number of images to process is large and growing.

In these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.
Furthermore, the value of the answer depends on the target application.

\begin{figure}[ht!]
\center{\includegraphics[width=0.86\linewidth]
    {../figures/figure1.pdf}}
  \caption{
A sample trace of our method.
At each time step beginning at $t=0$, potential actions are considered according to their \emph{value}, and the one with the highest value is picked.
The selected action is performed and returns observations, which influence the selection of the next action.
The final evaluation of a detection episode is the area of the AP vs. Time curve between the start and end times.
The value of an action is the expected value of the final evaluation if the action is taken and the policy continues to be followed, which allows actions without an immediate benefit to be scheduled.
}
  \label{fig:figure1}
\end{figure}

A hypothetical recognition system for a vision-based advertising deployment presents a case study.
The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
The detection strategy to maximize profit in such an environment should depend on all of these variables.

We argue that the key to tackling such problems of dynamic recognition resource allocation is to start asking a new question:
\emph{What is the best performance we can get on a budget?}
To answer it, we consider the evaluation metric of performance vs. time, shown in Figure~\ref{fig:figure1} and discussed further in the text.

We present a method that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
We are able to obtain better performance than baselines when there is less time available than is needed to run all detectors.

### 2012-06-01 writeups/nips12/nips2012.tex
draft for mario

\begin{abstract}
In a large visual multi-class detection system, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and that the best answer must be given by some deadline.
Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic policy guided by inference of the contents of the image to decide which detector to deploy next.
We evaluate with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC object detection dataset.
\end{abstract}

@@

>>>>

\begin{abstract}
In a large visual multi-class detection framework, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
Our method for multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic, \emph{closed-loop} policy guided by inference of the contents of the image in order to decide which detector to deploy next.
We evaluate our method with respect to performance in the novel Average Precision (AP) vs. Time evaluation on the widely used PASCAL VOC object detection dataset.
With our method, if execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
Overall, our method obtains at least $11\%$ better performance on the AP vs. Time evaluation.
\end{abstract}

@@

\section{Conclusion}
We presented a method for learning ``closed-loop'' policies for multi-class object recognition, given existing object detectors and classifiers and a metric to optimize.
The method learns the optimal policy using reinforcement learning, by observing execution traces in training.
If detection on an image is cut off after only half the detectors have been run, our method does $66\%$ better than random, and $14\%$ better than an intelligent baseline.

As always with reinforcement learning problems, the setting of the reward function requires some manual work.
Here, we derive it for the novel detection AP vs. Time evaluation that we suggest is most useful for evaluating efficiency in recognition.
Although computation devoted to scheduling actions is much less significant than the computation due to running the actions, an interesting future research direction is to explicitly consider this decision-making cost.

### 2012-06-01 writeups/nips12/related.tex
draft for mario

We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains at least one, and often multiple, objects.
Each object is labeled with exactly one category label $k \in \{1, \dots, K\}$.

@@

Window proposal is often done exhaustively over the image space, as a ``sliding window''.
Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Vedaldi2009,Vijayanarasimhan2011}.
For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008b}.

@@

A state-of-the-art detector builds upon a linear classifier on a gradient-based image representation, sped up with cascaded evaluation (see relevant paragraph further down) \cite{Felzenszwalb2010b}.
Our system employs these detectors.

\paragraph{Context}
Context has a long history in vision.
One source of context is the scene or other non-detector cues; for the commonly used PASCAL dataset, these are quantitatively explored in~\cite{Divvala2009}. 
The most common scene-level feature is the GIST \cite{Oliva2001a} of the image; it provides reasonable information for scene classification \cite{Xiao2010a}.

Another source is inter-object context, used for detection in a random field setting in~\cite{Torralba2004}.
Exploiting this information has shown to improve classification as well as detection tasks.
A critical summary of the main approaches to using context for object and scene recognition is given in \cite{Galleguillos2010}.

\paragraph{Multi-Class Detection}
Inherently multi-class detection has its own line of work, which focuses largely on making detection time sublinear in the number of classes, through sharing features~\cite{Torralba2007,Fan2005,Razavi2011}.
A proposed post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression~\cite{Desai2009}.

\paragraph{Cascades}
An early success in efficient object detection used simple, fast features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime~\cite{Viola2001}.
Although the simple features and classifiers of this method have been surpassed by more complex detectors, the idea of cascading classifier evaluations is still often used.
Most recently, cyclic optimization has been applied to optimize cascades with respect to feature computation cost as well as classifier performance \cite{Chen2012}.

@@

\paragraph{Anytime Algorithms and Active Classification}
Although an important concept, anytime performance in vision systems is a surprisingly little-explored idea \cite{Shlomo Zilberstein}.
A recent application to the problem of visual detection picks features with maximum value of information in a Hough-voting framework, and explicitly evaluates performance vs. time \cite{Vijayanarasimhan2010}.

There has also been work on active classification \cite{Gao2011} and active sensing \cite{Yu2009}, in which intermediate results are considered in order to decide on the next classification step.
This line of work is closest to our approach.
Most commonly, the scheduling is greedy with respect to some quantity such as expected information gain.

In contrast, we are able to learn policies that take actions without any immediate such reward.
We aim for a general system that can take black-box detectors and classifiers, and learn its policy from its own trial execution traces, and can be adapted to different loss functions.

>>>>

We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains zero or more objects.
Each object is labeled with exactly one category label $k \in \{1, \dots, K\}$.

@@

Window proposal is often done exhaustively over the image space, as a ``sliding window''.
Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Vedaldi2009,Vijayanarasimhan2011}.
For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008a}.

@@

\paragraph{Context}
Context has a foundational role in vision.
One source of context is the scene or other non-detector cues; the most common scene-level feature is the GIST \cite{Oliva2001a} of the image.
For the commonly used PASCAL VOC dataset \cite{pascal-voc-2010}, GIST and other sources of context are quantitatively explored in~\cite{Divvala2009}.

Another source is inter-object context, shown to be useful for improving detection \cite{Torralba2004}.
A critical summary of the main approaches to using context for object and scene recognition is given in \cite{Galleguillos2010}.

\paragraph{Multi-Class Detection}
Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005,Razavi2011}.
A proposed post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression \cite{Desai2009}.

\paragraph{Cascades}
An early success in efficient object detection used simple, fast features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime \cite{Viola2001}.
Although the simple features and classifiers of this method have been surpassed by more complex detectors, the idea of cascading classifier evaluations is still often used.
Most recently, cyclic optimization has been applied to optimize cascades with respect to feature computation cost as well as classifier performance \cite{Chen2012}.

@@

\paragraph{Anytime Algorithms and Active Classification}
Anytime performance in vision systems is a surprisingly little-explored idea.
A recent application to the problem of visual detection picks features with maximum value of information in a Hough-voting framework, and explicitly evaluates performance vs. time \cite{Vijayanarasimhan2010}.

There has also been work on active classification \cite{Gao2011} and active sensing \cite{Yu2009}, in which intermediate results are considered in order to decide on the next classification step.
This line of work is closest to our approach.
Most commonly, the scheduling in these approaches is greedy with respect to some quantity such as expected information gain.

In contrast, we are able to learn policies that take actions without any immediate reward.
